##################################################################
### Sept 20, 2018
### Anusheh Kafi
### Homework 2
##################################################################

---
title: "p8105_hw1_ak4123"
output: github_document
---
## __Question 1__

### _A. Create dataframe_
```{r Dataframe_1}
library(tidyverse)
set.seed(1234)
question1_df = tibble(
  vec.numeric = runif(n = 10, min = 0, max = 5),
  vec.logical = c(vec.numeric > 2),
  vec.char = c("My", "name", "is", "Anu", "and", "this", 
               "is", "my", "homework", "attempt"),
  vec.factor = factor(c("male", "male", "female", "female", "male", 
                        "male", "female", "female", "male", "male"))
)
```

### _B. Mean of the each variable in the dataframe_
```{r means}
mean(question1_df$vec.numeric)
mean(question1_df$vec.logical)
mean(question1_df$vec.char)
mean(question1_df$vec.factor)
```
#### The mean of the numeric vector is 2.446132. This was able to work because we are just taking the mean of numeric values.
#### The mean of the logical vector is 0.7. This was able to work because things labelled as True were counted as 1 and False were counted as 2, then the mean was taken of these numeric values.
#### The mean of the character variable is not available. We are unable to take a mean of this variable because it is not numeric or logical
#### The mean of the factor variable is not available. We are unable to take a mean of this variable because it is not numeric or logical.

###_C. Apply the as.numeric function to the logical, character, and factor variables_
```{r results = 'hide'}
as.numeric(question1_df$vec.logical)
as.numeric(question1_df$vec.char)
as.numeric(question1_df$vec.factor)
```
#### By applying the as.numeric function to the logical variable, the entries that should be false are made a 0 and the ones that should be a true are made a 1.
#### By applying the as.numeric function to the character variable, the entries were all turned into NA.
#### By applying the as.numeric function to the factor variable, the entries that should be male are made a 2 and the ones that should be a woman are made a 1. 

### _D. Convert character variable from character to factor to numeric and convert factor variable from factor to character to numeric_
```{r coercion_step_2}
as.numeric(as.factor(question1_df$vec.char))
as.numeric(as.character(question1_df$vec.factor))
```
#### Converting the character vector into a factor vector then into a numeric vector turned the character words each into a factor (so it assigned each word a factor) then each factor was given a number when it got convered to numeric. For example, two of the same words were assigned a 5. 
#### Converting the factor vector into a character vector then into a numeric vector simply produced N/A for all the entries, as the factors were unable to be converted to characters. 

## __Question 2__

### _A. Create dataframe_
```{r dataframe_2}
set.seed(1234)

question2_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec.logical =  x + y > 0,
  vec.numeric = as.numeric(vec.logical),
  vec.factor = as.factor(vec.logical)
)  
```
### _B. Description of dataset_
`r {dim(question2_df)}` is the dimensions of this dataset.
`r {mean(question2_df$x)}` is the mean of x and `r {median(question2_df$x)}` is the median of x. 
`r {mean(question2_df$vec.logical)}` is the proprtion of cases for which the logical vector is TRUE 

### _C. Scatterplot of y vs x -- Color scale: Logical Vector_
```{r scatterplot_1}
ggplot(question2_df, aes(x = x, y = y, color = vec.logical)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```
#### Color Scale (Plot 1): Green is x+y is greater than 0 and Red is x+y is not greater than 0. This plot was saved using the ggsave function. 

### _D. Scatterplot of y vs x -- Color scale: Numeric_
```{r scatterplot_2}
ggplot(question2_df, aes(x = x, y = y, color = vec.numeric)) + geom_point()
```
#### Color Scale (Plot 2): The colors are a range, the darkest blue/black is 0.00 and the lightest blue is 1.00

### _E. Scatterplot of y vs x -- Color scale: Factor_
```{r scatterplot_3}
ggplot(question2_df, aes(x = x, y = y, color = vec.factor)) + geom_point()
```
#### Color Scale (Plot 3): Green is True, Red is False  

